Large squeezing in multicomponent trapped Bose-Einstein condensates

### 2012-11-16 large_number_squeezing_with_atoms.tex
Add figure showing some analytic two-mode solutions
Also remove the [12pt] option so we're using the publication
layout rather than the proof layout, so we can get a better
idea of how long the paper will be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}
\usepackage{graphicx}
\usepackage{ulem}

@@

While the analytic expressions for the number variances are not particularly edifying, it is easy to evaluate and plot them for any given set of parameters. As an example, in Figure \ref{figxxx} we plot the solution for the normalized number variance in mode $|a\rangle$ for a particular set of nonlinearities, choosing a number of different values of $\phi$. The plots illustrate the basic features of the problem: During the final coupling period, the number variance undergoes cyclic variation, with a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass{iopart}
%\newcommand{\gguide}{{\it Preparing graphics for IOP journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}
\usepackage{graphicx}
\usepackage{ulem}

@@

While the analytic expressions for the number variances are not particularly edifying, it is easy to evaluate and plot them for any given set of parameters. As an example, in Figure \ref{figTwoModeAnalyticExamples} we plot the solution for the normalized number variance in mode $|a\rangle$ for a particular set of nonlinearities, choosing a number of different values of $\phi$. The plots illustrate the basic features of the problem: During the final coupling period, the normalised number variance undergoes cyclic variation with a period $\tau=0.5 \Omega$, and has a series of minima. It is necessary to choose both the correct phase $\phi$ as well as the correct length of time for the coupling to be applied in order to obtain optimum squeezing.

@@

\begin{figure}
    \centering
    \includegraphics[width=10cm]{figures/analytic_two_mode_examples.eps}
    \caption{Normalized number variance Var$[N_a]/N_a$ in mode $\hat{a}$ as a function of final recombination time plotted on a logarithmic scale, using four different mixing angles $\phi$. Parameters: $n_a = n_b =5 \times 10^5$, $\chi_{aa}=0.04 \hbar, \chi_{ab}=0, \chi_{bb}=0.01\hbar, \tau_{\mathrm{hold}}=4\times 10^{-4}$s. Solid line, $\phi=0.10$; dash-dotted line, $\phi=1.42$; dashed line, $\phi=3.24$; dotted line, $\phi=4.71$.} 
    \label{figTwoModeAnalyticExamples}
\end{figure}
